The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
init clump

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be core helium-burning red clump stars. A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}.

>>>>

Red clump stars, which burn helium in their cores, differ significantly in their core structure from stars on the hydrogen shell burning red giant sequence. They can therefore be distinguished from hydrogen-shell burning giants asteroseismologically, due to their much higher \emph{g}-mode period spacings \citep{rggmodehelium}. 
The moniker `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}. This property makes them useful standard candles to which distances can be accurately computed from photometry. Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}. \gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and in particular hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}.
